\documentclass{article}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\usepackage{pgfplots}
\usepackage{amsmath}
\begin{document}

\section{ Understanding the difﬁculty of training deep feedforward neural networks \cite{Glorot2010}}
The fact that this article is cited almost 30,000 times is enough for it to be important in pretty much any AI research and it gives a much deeper look into the history of ANN's and how they can be used in many fields to simulate brain function in a sense and later down the line be able to create things such as LLM's. What Glorort and Bengio were able to find out about learning on infinite data-sets and getting AI to classify shaps and objects into 9 different classifications is a sort of basic use of ANN's in today's world going to show that the development of ANN's massivdly stemmed from this article and how this type of technology is even used in places like airports and other security checkpoints to help classify certain items as dangerous. The notes they have about training and what is needed to train an ANN are something that could come into play in my own project and it is important to learn about them.
\section{Logistic regression and artificial neural network classification \cite{Dreiseitl2002}}
This article talks more about logistic regression in comparison to ANN's which is something I was curious about because they are somewhat similar and both could be incorporated into the project. It is ahrd to tell how much overfitting could come into play in my own project but with logisitic regression already having low complexity in the model I figured it could be useful in that case. This articles also discusses a bit of how both can be used in the medical world and in that sense the ethics of data collection using both LR and ANN. This shouldn't really be an issue at all in my project but it is a good thing to note none the less. This article also goes into how ANN's handle interactions better in most cases which leads me to think that for creating a driver behavior model, an ANN would likely be better for all aspects of the project.
\section{ State-of-the-art in artificial neural network applications: A survey \cite{Abiodun2018}}
This is a more current article about how ANN's can really be used in a very wide range of uses specifically for classification, pattern recognition, and most important predicting. It goes in depth about how pretty much every single major company that does anything with tech whatsoever is using ANN's and how if they aren't they should. They go on to elaborate how a lot of operations research jobs should simply be reaplced by ANN's as they will be able to tell you much more than a human ever would be able to. It also goes in depth about how it is menat to simulate the function of the human brain similar to the Bengio article and that makes so much sense for creating a driver bahevaior mdoel when you look at it like that because driver behavior is literally a brain function. It doesn't help too much in how that could be used for a driver behavior model but in theory with the right inputs and right learning functions, I see no reason why an ANN should not be used for this model I plan on creating. The only issue would be figuring out how to get it into Assetto Corsa and run hundreds of times without blowing up my laptop. 
\bibliographystyle{plain}
\bibliography{export.bib}
\end{document}